DCVtestkit Output Examples

### 2022-10-10 README.qmd
Add additional text.

---
title: "DCVtestkit Output Examples"
format: 
  gfm:
    author: Jeremy Selva
    date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

---
title: "DCVtestkit Output Examples"
format: gfm
---

# Introduction

Here is where I store some output example of the R package [`DCVtestkit`](https://github.com/SLINGhub/DCVtestkit)

## Excel Output Example

[`dilution_summary.xlsx`] is the output in Excel.

## Pdf Output Example

[`dilution_plot.xlsx`] is the output in pdf.

## Trellis Output Example

https://dcvtestkit-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.

## Quarto Output Example

https://dcvtestkit-quarto-example.netlify.app is the output of a html file generated using [Quarto](https://quarto.org/)
